INTELLIGENT SYSTEMS

### 2021-04-08 paper_5.tex
finish paper5

\subsection{INTRODUCTION}
An individual's gait appears as their own fingerprint. The study of this 
topic doesn't not only concern the area of medicine, but also that of security 
and identification. The gating study is based on a non-invasive system that 
collects patterns without the direct intervention of the subject. The data, 
which allow the recognition of the gait, are taken by inertial sensors present 
in a multitude of devices such as smartphones or smartwatches. A system 
is presented that uses a convolutional neural network (CNN) that uses the 
data collected by these inertial sensors to be able to predict the subject. The 
approach followed is the one in figure \ref{fig:preview}. Two extensions have been added 
to the network. The first deals with merging sensory data, while the second 
deals with improving the learning process and producing multiple outputs 
from a single input, thanks to a multi-task scheme. The tasks considered 
are: identification, gender recognition and age estimation. The dataset used 
is OU-ISIR gait database \cite{0857651721}, containing information such as inertial sensors 
such as accelerometers and gyroscopes.
\begin{figure}[htbp]
    \centering
    \includegraphics[width = 0.6 \linewidth]{images/paper5/usecase.png}
    \centering
    \caption{A preview of how the model works.}
    \label{fig:preview}
\end{figure}

@@

\subsubsection{Gait Recognition experiments}
Different types of experiments and their respective performances, in terms of accuracy and F1-measure, are presented below.
\begin{enumerate}
    \item \emph{Sensor position}: the following experiment show that using 3 different 
    sensors, the model has greater accuracy and a high value of F1-measure, 
    when using data from the sensor positioned on the left side of the body.
    \begin{table}[h!]
        \centering
        \begin{adjustbox}{max width=\textwidth}
        \begin{tabular}{*{3}{|c}|}%%{|c|c|c|}
            \hline
            IMU Position & Acc & F1-score \\
            \hline
            center & 92.3 & 90.8\\
            left & \bfseries{95.2} & \bfseries{94.0}\\
            right & 91.5 & 90.0\\
            \hline
        \end{tabular}
        \end{adjustbox}
        \caption{Accuracy and F1-score of three different sensors.}
        \label{table accuracy and F1}
    \end{table}

@@

\subsubsection{Authentication Experiments}
In paragraph \ref{IA} we said that to see if two different samples belong to the 
same subject, an identity authentication process must be carried out. In 
other words, it is necessary to evaluate the goodness of a model by calculating 
the AUC and EER index. To do this, one had to first calculate the 
Euclidean distances between the sample vector present in the test set with 
the sample vectors present in the training set. Subsequently, it was necessary 
to transform these distances into probabilities that will be represented 
on a ROC curve. Once this is done, for each model previously described, 
the values for AUC (the higher the better) and EER (the lower the better), 
calculated on the ROC curve, are shown in table \ref{Authentication}. 
\begin{table}[h!]
    \centering
    \begin{adjustbox}{max width=\textwidth}
    \begin{tabular}{|c|cc|}
        \hline
        Architecture & EER & AUC\\
        \hline
        SingleTask Accelerometer & 1.47 & 99.91\\
        SingleTask Gyroscope & 2.50 & 99.80\\
        \hline
        MultiTask Accelerometer & 1.61 & 99.90\\
        MultiTask Gyroscope & 2.85 & 99.72\\
        \hline
        SingleTask Fusion & \bfseries{1.14} & \bfseries{99.93}\\
        \hline
        MultiTask Fusion & 1.34 & 99.92\\
        \hline
    \end{tabular}
    \end{adjustbox}
    \caption{Authentication accuracy.}
    \label{Authentication}
\end{table}

>>>>

\subsection{INTRODUCTION}
An individual's gait appears as their own fingerprint. The study of this 
topic doesn't not only concern the area of medicine, but also that of security 
and identification. The gating study is based on a non-invasive system that 
collects patterns without the direct intervention of the subject. The data, 
which allow the recognition of the gait, are taken by inertial sensors present 
in a multitude of devices such as smartphones or smartwatches. A system 
is presented that uses a convolutional neural network (CNN) that uses the 
data collected by these inertial sensors to be able to predict the subject. The 
approach followed is the one in figure \ref{fig:preview}. Two extensions have been added 
to the network. The first deals with merging sensory data, while the second 
deals with improving the learning process and producing multiple outputs 
from a single input, thanks to a multi-task scheme. The tasks considered 
are: identification, gender recognition and age estimation. The dataset used 
is OU-ISIR gait database \cite{0857651721}, containing information such as inertial sensors 
such as accelerometers and gyroscopes. Gait recognition can be used in two contexts:
\begin{enumerate}
    \item {\bfseries{Identification}}: gait is used to obtain the identity of a known subject.
    \item {\bfseries{Authentication}}: gait is used to validate the identity of a known subject.
\end{enumerate}
\begin{figure}[htbp]
    \centering
    \includegraphics[width = 0.6 \linewidth]{images/paper5/usecase.png}
    \centering
    \caption{A preview of how the model works.}
    \label{fig:preview}
\end{figure}

@@

\subsubsection{Gait Recognition experiments}
Different types of experiments on recognition, and their respective performances, in terms of accuracy and F1-measure, are presented below.
\begin{enumerate}
    \item \emph{Sensor position}: the following experiment show that using 3 different 
    sensors, the model has greater accuracy and a high value of F1-measure, 
    when using data from the sensor positioned on the left side of the body.
    \begin{table}[h!]
        \centering
        \begin{adjustbox}{max width=\textwidth}
        \begin{tabular}{*{3}{|c}|}%%{|c|c|c|}
            \hline
            IMU Position & Acc & F1-score \\
            \hline
            center & 92.3 & 90.8\\
            left & \bfseries{95.2} & \bfseries{94.0}\\
            right & 91.5 & 90.0\\
            \hline
        \end{tabular}
        \end{adjustbox}
        \caption{Accuracy and F1-score of three different sensors.}
        \label{table accuracy and F1}
    \end{table}

@@

\subsubsection{Authentication Experiments}
In paragraph \ref{IA} we said that to see if two different samples belong to the 
same subject, an identity authentication process must be carried out. In 
other words, it is necessary to evaluate the goodness of a model by calculating 
the AUC and EER index. To do this, one had to first calculate the 
Euclidean distances between the sample vector present in the test set with 
the sample vectors present in the training set. Subsequently, it was necessary 
to transform these distances into probabilities that will be represented 
on a ROC curve. Once this is done, for each model previously described, 
the values for AUC (the higher the better) and EER (the lower the better), 
calculated on the ROC curve, are shown in table \ref{Authentication}. From the results shown 
in the table, the multitask model obtains worse performance than the singletask 
model, this is caused by the fact that in the multitask model the labels 
to be managed are many more than the single label (id) to be managed in 
the singletask model.
\begin{table}[h!]
    \centering
    \begin{adjustbox}{max width=\textwidth}
    \begin{tabular}{|c|cc|}
        \hline
        Architecture & EER & AUC\\
        \hline
        SingleTask Accelerometer & 1.47 & 99.91\\
        SingleTask Gyroscope & 2.50 & 99.80\\
        \hline
        MultiTask Accelerometer & 1.61 & 99.90\\
        MultiTask Gyroscope & 2.85 & 99.72\\
        \hline
        SingleTask Fusion & \bfseries{1.14} & \bfseries{99.93}\\
        \hline
        MultiTask Fusion & 1.34 & 99.92\\
        \hline
    \end{tabular}
    \end{adjustbox}
    \caption{Authentication accuracy.}
    \label{Authentication}
\end{table}

\subsubsection{State of art comparison}
Comparing the proposed system with those already existing in the state of 
art, both for gait recognition (Tab.\ref{Gait comparison}) and authentication (Tab.\ref{Authentication comparison}), the 
performances outperforms those of the competitors.
\begin{table}[h!]
    \centering
    \begin{adjustbox}{max width=\textwidth}
    \begin{tabular}{|c|ccc|c|}
        \hline
        CNN & Id & Age & Gender & Avg\\
        \hline
        AE-GDI-CC & 61.0 & - & - & -\\
        Muaaz et al. & 63.5 & - & - & -\\
        Ngo et al. & 70.2 & - & - & -\\
        Wei et al. & 83.8 & - & - & - \\
        \hline
        MultiTask Fusion & \bfseries{94.8} & \bfseries{96.1} & \bfseries{97.7} & \bfseries{96.2}\\
        \hline
    \end{tabular}
    \end{adjustbox}
    \caption{Gait recognition comparison with some methods.}
    \label{Gait comparison}
\end{table}

\begin{table}[h!]
    \centering
    \begin{adjustbox}{max width=\textwidth}
    \begin{tabular}{|c|c|}
        \hline
        Approach & EER\\
        \hline
        Gafurov et al. & 15.8 \\
        Derawi et al. & 14.3 \\
        Rong et al. & 14.3 \\
        Ngo et al. & 13.5 \\
        Imp GDI + i-vector & 7.1 \\
        NC GDI + i-vector & 5.6 \\
        \hline
        SingleTask Fusion & \bfseries{1.1}\\
        \hline
    \end{tabular}
    \end{adjustbox}
    \caption{Authentication comparison with some methods.}
    \label{Authentication comparison}
\end{table}

\subsubsection{Execution time during test}
MultiTask models are the most time-consuming, but it is also true that they 
produce three outputs simultaneously (Fig. \ref{fig:time}).
\begin{figure}[htbp]
    \centering
    \includegraphics[width = 0.6 \linewidth]{images/paper5/time.png}
    \centering
    \caption{Execution time of the proposed models}
    \label{fig:time}
\end{figure}

\subsection{CONCLUSIONS}
As a final consideration, the model to be used, in the case of gait recognition, 
is the one that merges the input information and adopts a multitask 
approach. On the other hand, as regards the authentication problem, it has 
been seen that it is better to use a singletask model.
